\chapter{攻读学位期间研究成果}

\IfStrEq{\Version}{Anonymous}{

\section*{第一作者:}
\begin{enumerate}[label={[\arabic*]}]
  \item \textit{2024 IEEE Transactions on Circuits and Systems II: Express Briefs. （在投）}
  \item \textit{2023 IEEE International Conference on Field-Programmable Technology (ICFPT).}
  \item \textit{IEEE Transactions on Very Large Scale Integration (VLSI) Systems, 2022.}
  \item \textit{2022 IEEE International Symposium on Circuits and Systems (ISCAS).}
\end{enumerate}

\vspace{5pt}
\section*{合著作者：}
\begin{enumerate}[label={[\arabic*]}]
  \item 第二作者， \textit{2024 IEEE  International Symposium of Electronics Design Automation (ISEDA).}
  \item 第三作者， \textit{2023 IEEE  International Conference on ASIC (ASICON).}
  \item 第三作者， \textit{2023 IEEE  International Symposium of Electronics Design Automation (ISEDA).}
  \item 第四作者， \textit{2022 IEEE International Symposium on Circuits and Systems (ISCAS).}
  \item 第三作者， \textit{2021 IEEE International Conference on Field-Programmable Technology (ICFPT).}
\end{enumerate}

}{

\section*{第一作者（含共同一作）:}
\begin{enumerate}[label={[\arabic*]}]
  % \item \textbf{Li Z}, Zhu Kaixiang, et al. An Open-source End-to-End Logic Optimization Framework for Large-scale Boolean Network with Reinforcement Learning[J]. IEEE Transactions on Circuits and Systems II: Express Briefs, 2024. （在投）
  \item \textbf{Li Z}, Zhou H, Wang L, et al. AMG: Automated Efficient Approximate Multiplier Generator for FPGAs via Bayesian Optimization[C]//2023 International Conference on Field Programmable Technology (ICFPT). IEEE, 2023: 294-295.
  \item \textbf{Li Z}, Zheng S, Zhang J, et al. Adaptable Approximate Multiplier Design Based on Input Distribution and Polarity[J]. IEEE Transactions on Very Large Scale Integration (VLSI) Systems, 2022, 30(12): 1813-1826.
  \item Zheng S, \textbf{Li Z}, Lu Y, et al. HEAM: High-efficiency approximate multiplier optimization for deep neural networks[C]//2022 IEEE International Symposium on Circuits and Systems (ISCAS). 2022: 3359-3363.
\end{enumerate}

\vspace{5pt}
\section*{合著作者：}
\begin{enumerate}[label={[\arabic*]}]
  \item Li K, \textbf{Li Z}, Wang L. TLED: Training-Based Approximate Layer Exploration in DNNs with Efficient Multipliers[C]// 2024 International Symposium of Electronics Design Automation (ISEDA). IEEE, 2024.
  \item Li K, Dai Y, \textbf{Li Z}, et al. Permutation-Based Approximate Multiplier with High Accuracy[C]//2023 IEEE 15th International Conference on ASIC (ASICON). IEEE, 2023: 1-4.
  \item Shi X, Yang M, \textbf{Li Z}, et al. Exploration of FPGA PLB Architecture Base on LUT and Microgates[C]//2023 International Symposium of Electronics Design Automation (ISEDA). IEEE, 2023: 184-189.
  \item Lu Y, Zhang J, Zheng S, \textbf{Li Z}, et al. Low Error-Rate Approximate Multiplier Design for DNNs with Hardware-Driven Co-Optimization[C]//2022 IEEE International Symposium on Circuits and Systems (ISCAS). IEEE, 2022: 3507-3511.
  \item Wang X, Yang M, \textbf{Li Z}, et al. Parallelized Technology Mapping to General PLBs by Adaptive Circuit Partitioning[C]//2021 International Conference on Field-Programmable Technology (ICFPT). IEEE, 2021: 1-5.
\end{enumerate}

}